---
title: "Age*Cognition and Clincal Symptom GAMM Interaction models"
author: "Bart"
date: "2/28/2019"
output:
  html_document: default
  toc: true
  # pdf_document: default
---

# Modeling the effect of continuous interactions of covariates with `age` on `R2s`
This code implements best practices for continuous x continuous GAMM models as decided upon in Psychosis_GAMM_v3.rmd
Paraphrasing the technique:  
> "Use `gamm` with smoothed main effects and bivariate interactions modeled with tensor product interaction smooths, `ti`. Models use fixed *df* for smooth terms and parametric bootstrapping is done to test all nested models."  
---

```{r setup, include=FALSE}
## Load Libraries
require(ggplot2)
require(gridExtra)
require(tidyverse)
require(mgcv)
require(gamm4)
require(mgcViz)
require(sjPlot)
require(pbkrtest)
require(itsadug)
library(broom)
library(kableExtra)
library(parallel)
library(scales)
source('~/projects/brain_iron/TakiMeeting/plotGAMM_Bart.R')
source('/Users/larsenb/software/ComBatHarmonization-master/R/scripts/combat.R')
source('/Users/larsenb/software/ComBatHarmonization-master/R/scripts/utils.R')
knitr::opts_knit$set(root.dir = "/data/jux/BBL/projects/brain_iron/scripts/analysis/")
theme_set(theme_classic())
```

```{r make cluster, include=F}
 
# library(doParallel)
cl <- makeCluster(rep("localhost",20))
# registerDoParallel(cl)
```
 
## Relevant functions:
### GAMM modeling
```{r gamm}
gamm_model <- function(df, model_formula, this_label, smooth_var, int_var = NULL,weight_var = NULL,group_var, pbootstrap = F, longPlot = F){
  cat(sprintf("\n\n### Results for %s\n",this_label))
  if (is.null(weight_var)) {
    df$weight <- 1
  } else {
    df$weight <- unlist(df[,weight_var])
  }

  model_formula <- as.formula(model_formula)
  if(!"exclusions" %in% colnames(df))  {
    df$exclusions <- FALSE; #there is no exclusions column so make one that excludes none
  }

  g1<-gamm(model_formula,
           data=df,
           random = list(bblid =~ 1),
           subset = exclusions == F,
           weights = weight)
  if (pbootstrap == T) {
    g1$pb<-pboot(g1)
    print(g1$pb %>%
      summary() %>%
      .$test %>%
      as.data.frame() %>%
      kable(caption = sprintf("Parametric Bootstrap test for %s",this_label)) %>%
      kable_styling(full_width = F, position = "left",bootstrap_options = c("striped"))
    )
    
    if (isTRUE(all.equal(g1$pb$bestmod,model_formula))) {
      cat("The initial (more complicated) model is best")
      g <- g1
      # t<-terms(g1$gam$formula)
      # tnew <- drop.terms(t,2:3,keep.response = T)
      # rightside<-as.character(reformulate(attr(tnew,"term.labels")))[2]
      # rightside <- rightside %>% gsub("ti","te",.) %>% gsub("fx = T","fx = F",.)
      # plot_formula <- as.formula(sprintf("R2s ~ %s",rightside))
      if (str_detect(deparse(model_formula),"F1_Social_Cognition_Efficiency") &this_label == "Right_Pallidum_male") {
        plot_formula <- model_formula
      } else {
      plot_formula <- as.formula(gsub(", fx = T","",deparse(model_formula)))
      }
      cat(deparse(plot_formula))
      plotg<-g
      # plotg <- gamm(plot_formula,
      #               data = df,
      #               random = list(bblid =~1),
      #               subset = exclusions == F)
    } else {
      cat("The simpler model is best")
      
      g <-gamm(as.formula(g1$pb$bestmod),
               data=df,
               random = list(bblid =~ 1),
               subset = exclusions == F,
               weights = weight)
      plot_formula <- as.formula(gsub("ti\\(",'te\\(',deparse(g$gam$formula)) %>% gsub(", fx = T", "", .))
      plotg<-g
      # plotg <-gamm(plot_formula,
      #          data=df,
      #          random = list(bblid =~ 1),
      #          subset = exclusions == F)
    }
  } else {
    if (!is.null(int_var)) {
      s<-summary(g1$gam)
      if (s$s.table[grep(x=rownames(s$s.table),pattern = int_var),"p-value"] <.505)  {
        g <- g1
        plot_formula <- as.formula(gsub(", fx = T", "", deparse(model_formula)))
        plotg <- g
      } else {
        cat("The simpler model is best")
        thisResp <- as.character(g1$gam$terms[[2]])
        theseVars <- attr(terms(model_formula),"term.labels")
        new_formula <- reformulate(theseVars[0:(length(theseVars)-1)],response = thisResp)
        
        g <-gamm(as.formula(new_formula),
                 data=df,
                 random = list(bblid =~ 1),
                 subset = exclusions == F,
                 weights = weight)
        plot_formula <- as.formula(gsub("ti\\(",'te\\(',deparse(g$gam$formula)) %>% gsub(", fx = T", "", .))
        plotg<-g
    }
    } else {
      g <- g1
        plot_formula <- as.formula(gsub(", fx = T", "", deparse(model_formula)))
        plotg <- g
    }
  }

  g$gam$data<-df %>%
    filter(exclusions == F)
  
  #Display model results
  #Send final model to visualizer:


  #cell_spec(.$p,bold = (ifelse(.$p < .05, "TRUE", "FALSE"))) %>%
  
  # s_tidytable<- tidy(g$gam) %>% 
  #   kable(caption = sprintf("Regression table for smooth terms from gamm in %s",this_label)) %>% 
  #   kable_styling(full_width = F, position = "left")
  # 
  # p_tidytable <- tidy(g$gam,parametric = T)%>% 
  #   kable(caption = sprintf("Regression table for parametric terms from gamm in %s",this_label)) %>% 
  #   kable_styling(full_width = F, position = "left")
  # print(p_tidytable)
  # print(s_tidytable)

  s_tidytable<- tidy(g$gam)
  p_tidytable <- tidy(g$gam,parametric = T)
  snames = names(s_tidytable)
  pnames = names(p_tidytable)
  names(s_tidytable)=pnames
  stattable <- rbind(p_tidytable,snames,s_tidytable) %>%
    kable(caption = sprintf("Regression table from gamm in %s",this_label)) %>% 
    kable_styling(full_width = F, position = "left")
  print(stattable)
  
  if (s_tidytable$p.value[nrow(s_tidytable)]<.05) {
    if (longPlot == T) {
      g$pl <- longitudinal_plot(g,plabels = this_label)
    } else {
      g$pl <- visualize_models(plotg,plabels = this_label, smooth_var = smooth_var, int_var = int_var, group_var = group_var)
    }
  }
  
  
  
  #Return result object
  result <- g
  
  return(result)
}
```

### Bootstrap procedure
This procedure is lifted from https://github.com/PennBBL/groupAnalysis/wiki/Model-Comparison-Using-Parametric-Bootstrap
```{r include=T,opts.label = "Bootstrap Function"}
## Parametric bootstrap of likelihood ratio test for nested models
pboot <- function(modelobj){
  numsims <- 500

  df <- modelobj$gam$model
  thisResp <- as.character(modelobj$gam$terms[[2]])
  f1 <- modelobj$gam$formula
  theseVars <- attr(terms(f1),"term.labels")
  f2 <- reformulate(theseVars[0:(length(theseVars)-1)],response = thisResp)
  
  g1 <- gam(f1,data = df,weights = `(weights)`)
  g2 <- gam(f2,data = df,weights = `(weights)`)

  mat1 <- model.matrix(g1)
  mat2 <- model.matrix(g2)

  bblid<-df$bblid
  y <- df[,thisResp]
  w <- unlist(df[,"(weights)"])
  
  m1 <- lmer(y ~ -1 + mat1 + (1|bblid),weights = w)
  m2 <- lmer(y ~ -1 + mat2 + (1|bblid),weights = w)
  cat("\ncreating bootstrap ref dist\n")
  refdist <- PBrefdist(m1, m2, nsim=numsims)#, cl=cl)
  cat("\nfinished bootstrap ref dist\n")
  pb <- PBmodcomp(m1, m2, ref = refdist)
  int_pval <- pb$test["PBtest","p.value"]
  if (int_pval < .05) {
    pb$bestmod <- f1
  } else {
    pb$bestmod <- f2
  }
  cat("\ngot best mod\n")
  return(pb)
}
```

```{r visual func, include=FALSE}
# Func to visualize model outputs
visualize_models <- function(modobj,smooth_var, int_var ,group_var, plabels = NULL,check_diagnostics = F){
  if (any(class(modobj)=="gam")) {
    model <- modobj
  } else if (class(modobj$gam)=="gam") {
    model <- modobj$gam
  } else {
    stop("Can't find a gam object to plot")
  }

  ## Plot using mgcViz functions
  #l_fitRaster(pTrans = function(.p) .p<0.05)
  b <- getViz(model)
  var_plot <- plot(b,allTerms = T) + 
    l_ciPoly() +
    l_fitRaster() + l_fitContour() + 
    l_points() +  l_ciBar() +
    l_fitPoints(size = 1, col = 2) + l_fitLine() +
    labs(title = plabels)
  # mtext(plabels, outer = TRUE, cex = 1.5)

  print(var_plot,pages = 1) 

  # line plot
  np <- 10000 #number of predicted values
  df = model$model

  theseVars <- attr(model$terms,"term.labels")
  varClasses <- attr(model$terms,"dataClasses")
  thisResp <- as.character(model$terms[[2]])

  if (!is.null(int_var)&any(grepl(x=as.character(model$formula),pattern = int_var))) {
    switch (varClasses[int_var],
      "numeric" = {
        q <- quantile(df[,int_var],probs = c(.05,.95))
        bigq <- q[[2]]
        smallq <- q[[1]]
        values <- c(bigq,smallq)
        labs <- c(sprintf("high (%1.2f)",bigq),sprintf("low (%1.2f)",smallq))

        #Get plot color break values
        # q <- quantile(df[,int_var],probs = c(0,.1,.5,.9,1))
        # break_values <- unname(q)
        # break_labels <- names(q)
        # limit_values <- c(q[[1]],q[[length(q)]])

        q <-quantile(rescale(df[,int_var],c(0,1)),probs = c(0,.5,1))
        limit_values <- c(q[[1]],q[[length(q)]])
        midpoint_val <- unname(q[[2]])
        cbar_vals <- unname(q)
        grad_fill = T
      },
      "factor" = {
        labs <- levels(df[,int_var])
        values <- levels(df[,int_var])
        grad_fill = F
      },
      "ordered" = {
        labs <- levels(df[,int_var])
        values <- levels(df[,int_var])
        grad_fill = F
      }
    )
    labPred <- data.frame(init = rep(0,np*length(labs)))
    labPred[,int_var] = rep(values,each = np)
    labPred$lab = rep(labs,each = np)
    labPred <- labPred[,names(labPred) !="init"]
    thisPred <- data.frame(init = rep(0,np))
    for (v in c(1:length(theseVars))) {
      thisVar <- theseVars[[v]]
      thisClass <- varClasses[thisVar]
      if (thisVar == smooth_var) {
        thisPred[,smooth_var] = seq(min(df[,smooth_var],na.rm = T),max(df[,smooth_var],na.rm = T), length.out = np)
      } else if (v == int_var) {
        next
      } else {
        switch (thisClass,
            "numeric" = {thisPred[,thisVar] = median(df[,thisVar])},
            "factor" = {thisPred[,thisVar] = levels(df[,thisVar])[[1]]},
            "ordered" = {thisPred[,thisVar] = levels(df[,thisVar])[[1]]}
              )
      }
    }

    thisPred <- thisPred %>% select(-init)
    thisPred <- do.call("rbind", replicate(length(labs), thisPred, simplify = FALSE))

    pred <- cbind(labPred,thisPred)
    p<-data.frame(predict(modobj$gam,pred,se.fit = T))
    pred <- cbind(pred,p)
    pred$selo <- pred$fit - 2*pred$se.fit
    pred$sehi <- pred$fit + 2*pred$se.fit
    pred[,group_var] = NA
    pred[,thisResp] = 1

    high_color = "#d73027"
    low_color = "#4575b4"
      #scale_color_gradientn(colors = c("blue4","blue","linen","red","red4"),limits = limit_values,breaks = break_values, labels = break_labels)
    #scale_fill_manual(values = c("red","blue")) +
    if (grad_fill == T) {
      p1 <- ggplot(data = df, aes_string(x = smooth_var,y = thisResp, color = int_var)) +
      geom_point(alpha = .6) + geom_line(aes(group = bblid),alpha = .6) +
      scale_color_gradientn(colors = c(low_color,high_color), values = cbar_vals) +
      geom_ribbon(data = pred,aes_string(x = smooth_var , ymin = "selo",ymax = "sehi", fill = "lab"),alpha = .5, linetype = 0) +
      scale_fill_manual(values = c(high_color,low_color)) +
      geom_line(data = pred,aes_string(x = smooth_var, y = "fit",group = "lab"),size =1) +
      labs(title = plabels, y = "R2*", x = "Age (years)", col = int_var)
    } else {
    p1 <- ggplot(data = df, aes_string(x = smooth_var,y = thisResp, color = int_var)) +
      geom_point(alpha = .6) + geom_line(aes(group = bblid),alpha = .6) +
      scale_color_brewer(type = "qual",palette = 6) +
      geom_ribbon(data = pred,aes_string(x = smooth_var , ymin = "selo",ymax = "sehi", fill = int_var),alpha = .5, linetype = 0) +
      scale_fill_brewer(type = "qual",palette = 6) +
      geom_line(data = pred,aes_string(x = smooth_var, y = "fit",group = int_var,color = int_var),size =1) +
      labs(title = plabels, y = "R2*", x = "Age (years)", col = int_var)
    }
    if (str_detect(plabels,"Accumbens")) {
      p1 <- p1 + ylim(10,35)
    } else if (str_detect(plabels,"Pallidum")) {
      p1 <- p1 + ylim(12,40)
    } else if (any(str_detect(plabels,c("Putamen","Caudate")))) {
      p1 <- p1 + ylim(10,25)
    }
  print(p1)
  } else {

  # line plot
    thisPred <- data.frame(init = rep(0,np))

    for (v in c(1:length(theseVars))) {
      thisVar <- theseVars[[v]]
      thisClass <- varClasses[thisVar]
      if (thisVar == smooth_var) {
        thisPred[,smooth_var] = seq(min(df[,smooth_var],na.rm = T),max(df[,smooth_var],na.rm = T), length.out = np)
      } else {
        switch (thisClass,
            "numeric" = {thisPred[,thisVar] = median(df[,thisVar])},
            "factor" = {thisPred[,thisVar] = levels(df[,thisVar])[[1]]},
            "ordered" = {thisPred[,thisVar] = levels(df[,thisVar])[[1]]}
              )
      }
    }
    pred <- thisPred %>% select(-init)
    p<-data.frame(predict(modobj$gam,pred,se.fit = T))
    pred <- cbind(pred,p)
    pred$selo <- pred$fit - 2*pred$se.fit
    pred$sehi <- pred$fit + 2*pred$se.fit
    pred[,group_var] = NA
    pred[,thisResp] = 1

    p1 <- ggplot(data = df, aes_string(x = smooth_var,y = thisResp)) +
      geom_point(alpha = .8) + geom_line(aes(group = bblid),alpha = .5) +
      geom_ribbon(data = pred,aes_string(x = smooth_var , ymin = "selo",ymax = "sehi"),alpha = .5, linetype = 0) +
      geom_line(data = pred,aes_string(x = smooth_var, y = "fit"),size =1) +
      labs(title = plabels, y = "R2*", x = smooth_var)
    if (str_detect(plabels,"Accumbens")) {
      p1 <- p1 + ylim(10,35)
    } else if (str_detect(plabels,"Pallidum")) {
      p1 <- p1 + ylim(12,40)
    } else if (any(str_detect(plabels,c("Putamen","Caudate")))) {
      p1 <- p1 + ylim(10,25)
    }
  print(p1)
}
  #
  # var_plot2 <- plot(sm(b,3)) + l_fitRaster(pTrans = function(.p) .p<0.05) + l_fitContour() + l_points()
  # print(var_plot2)
  # print(plotRGL(sm(b, 1), fix = c("z" = 0), residuals = F))

  if (check_diagnostics == T) {
    cp <- check(b,
    a.qq = list(method = "tnorm",
                a.cipoly = list(fill = "light blue")),
    a.respoi = list(size = 0.5),
    a.hist = list(bins = 10))
    print(cp)
  }
  return(var_plot)
}
```

```{r long vis, include = FALSE}

longitudinal_plot <- function(modobj,plabels = NULL){
  df <- modobj$gam$model
  thisResp <- as.character(modobj$gam$terms[[2]])

  pred.male <- data.frame(age = seq(min(df$age,na.rm = T),max(df$age,na.rm = T), length.out = 1000), oSex = 'male',visit = "1",sequence = "B0map_onesizefitsall_v3",oRace_bwo = "1")
  p<-data.frame(predict(modobj$gam,pred.male,se.fit = T))
  pred.male$fit = p$fit
  pred.male$selo = p$fit - 2*p$se.fit
  pred.male$sehi = p$fit + 2*p$se.fit
  pred.male[,thisResp] = 1
  pred.male$bblid=1
  
  pred.female <- data.frame(age = seq(min(df$age,na.rm = T),max(df$age,na.rm = T), length.out = 1000), oSex ='female', visit="1",sequence = "B0map_onesizefitsall_v3",oRace_bwo = "1")
  p<-data.frame(predict(modobj$gam,pred.female,se.fit = T))
  pred.female$fit = p$fit
  pred.female$selo = p$fit - 2*p$se.fit
  pred.female$sehi = p$fit + 2*p$se.fit
  pred.female[,thisResp] = 1
  pred.female$bblid=1

  # p1 <- ggplot(data = df,aes_string(x = "age", y = thisResp, group = "bblid",color = "oSex")) + 
  #   geom_ribbon(data = pred.male, aes(ymin=selo, ymax=sehi), fill = "blue", alpha = .3, linetype = 0,show.legend = F) +
  #   geom_line(data = pred.male,aes(x = age, y = fit), color = "blue",size = 1) +
  #   geom_ribbon(data = pred.female, aes(ymin=selo, ymax=sehi), fill = "red", alpha = .3, linetype = 0,show.legend = F) +
  #   geom_line(data = pred.female,aes(x = age, y = fit), color = "red",size = 1) +
  #   labs(title = plabels, y = "R2*", x = "Age (years)", col = "Sex") + ylim(min(pred.female$selo-.5),NA)
  
  # geom_point(alpha = .25) +
  p1 <- ggplot(data = df,aes_string(x = "age", y = thisResp, group = "bblid",color = "oSex")) +
    geom_line(alpha = .25) + geom_point(alpha = .25) +
    scale_color_manual(values = c("blue","red")) +
    geom_ribbon(data = pred.male, aes(ymin=selo, ymax=sehi), fill = "blue", alpha = .3, linetype = 0,show.legend = F) +
    geom_line(data = pred.male,aes(x = age, y = fit), color = "blue",size = 1) +
    geom_ribbon(data = pred.female, aes(ymin=selo, ymax=sehi), fill = "red", alpha = .3, linetype = 0,show.legend = F) +
    geom_line(data = pred.female,aes(x = age, y = fit), color = "red",size = 1) +
    labs(title = plabels, y = "R2*", x = "Age (years)", col = "Sex")  + ylim(min(pred.female$selo-.5),NA)
  if (str_detect(plabels,"Accumbens")) {
    p1 <- p1 + ylim(10,30)
  } else if (str_detect(plabels,"Pallidum")) {
    p1 <- p1 + ylim(15,32)
  } else if (any(str_detect(plabels,c("Putamen","Caudate")))) {
    p1 <- p1 + ylim(11,25)
  }
  
  print(p1)
}
```

```{r load data, warning=FALSE, include=FALSE}
dataFile <- "brain_iron_data_TEMPLATE.Rda"
if (file.exists(dataFile)) {
  dataTable <- readRDS(file=dataFile)
  dataTableN <- readRDS(file = "brain_iron_data_native.Rda")
}  else {
  source('compileData.R')
  compileData()
  dataTable <- readRDS(file=dataFile)
}

## See data overlaps
library(VennDiagram)
vdf <- dataTable %>% select(Left_Putamen,Psychosis,NAR_F1_Exec_Comp_Cog_Accuracy,GOOD)
venn.diagram(list(R2s = which(!is.na(vdf$Left_Putamen)), Clinical = which(!is.na(vdf$Psychosis)),Cognitive = which(!is.na(vdf$NAR_F1_Exec_Comp_Cog_Accuracy)), QA = which(!is.na(vdf$GOOD))),filename = "~/test.tiff",euler.d = TRUE,fill = c("red2","blue2","yellow2","green2"),alpha = c(.5,.5,.5,.5))
knitr::include_graphics("~/test.tiff")

 
## Filter
dataTable <- dataTable %>%
  filter(bblid != 110689)%>%
  filter(GOOD %in% c("1","2")) %>%
  filter(sequence != 'B0map_onesizefitsall_v3_T2S' & sequence != 'B0map_v4_matchedFOV') %>% # & sequence != "b0map_v4") %>%
  filter(!(ProjectName %in% c("DAY2_808799","FNDM1_810211","FNDM2_810211","NEFF_V2","NEFF_PILOT", "GRMPY_822831", "GRMPY_V2","GRMPY_V3")))%>%
  filter(age<35)
dataTable$SES_Factor <- ordered(as.numeric(dataTable$envSES>-.5),levels=c(0,1),labels=c("Low SES","High SES"))
dataTable$Efficiency_Factor <- ordered(cut(dataTable$NAR_Overall_Efficiency,
                                           breaks = quantile(dataTable$NAR_Overall_Efficiency,
                                                             probs = seq(0,1,length=4),
                                                             na.rm = T),
                                           labels = c("low","med","hi")),
                                       levels = c("low","med","hi"))
dataTable$thisSES_Factor <- cut(dataTable$envSES,breaks = quantile(dataTable$envSES,probs = seq(0,1,length=4),na.rm = T),labels = c("low","med","hi"))
dataTable$tanner_age_diff <- dataTable$age-dataTable$tanner_age
dataTable$tanner_pubic <- ordered(dataTable$tanner_pubic, levels = c(1,2,3,4,5))

# ## combat  Doesn't work :(
# comtable <- dataTable %>%
#   select(Caudate,Putamen,Accumbens_Area,Pallidum,sequence)%>%
#   drop_na()
# batch <- as.factor(comtable$sequence)
# ctab <- comtable%>%select(-sequence)
# comtable %>% group_by(sequence) %>% summarize(n = n())
# combatdata <- combat(ctab,batch,eb = F)

dataTableN <- dataTableN %>%
  filter(GOOD %in% c("1","2")) %>%
  filter(sequence != 'B0map_onesizefitsall_v3_T2S'& sequence != 'B0map_v4_matchedFOV') %>% # & sequence != "b0map_v4") %>%
  filter(age<35)

#filter((!is.na(Psychosis) | !is.na(NAR_Overall_Accuracy)) & bblid != 110689) %>%
mtab<-dataTable %>%
  gather(key = "ROI",value="R2s",Accumbens_Area,Putamen,Caudate,Pallidum)
stab <-dataTable %>%
  gather(key = "ROI",value="R2s_sd",Accumbens_Area_sd,Putamen_sd,Caudate_sd,Pallidum_sd)%>%
  select(bblid,scanid,ROI,R2s_sd)
stab$ROI <- gsub(stab$ROI,pattern="_sd",replacement = "")
longTable <- mtab %>%
  left_join(stab,by = c("bblid","scanid","ROI"))
longTable$timepoint <- as.factor(longTable$timepoint)
longTable <- longTable %>%
  mutate(R2s_cv = R2s_sd/R2s)

# mtab<-dataTableN %>%
#   gather(key = "ROI",value="R2s",Accumbens_Area,Putamen,Caudate,Pallidum)
# stab <-dataTableN %>%
#   gather(key = "ROI",value="R2s_sd",Accumbens_Area_sd,Putamen_sd,Caudate_sd,Pallidum_sd)%>%
#   select(bblid,scanid,ROI,R2s_sd)
# stab$ROI <- gsub(stab$ROI,pattern="_sd",replacement = "")
# longTableN <- mtab %>%
#   left_join(stab,by = c("bblid","scanid","ROI"))
# longTableN$timepoint <- as.factor(longTable$timepoint)
# longTableN <- longTableN %>%
#   mutate(R2s_cv = R2s_sd/R2s)

```

---
# Developmental effects
```{r developmental, results="asis",eval=F}
# model_formula <- "R2s ~ sequence + oSex + RACE + s(age,k=4, fx=T) + s(age, k=4, fx = T, by = oSex)"
model_formula <- "R2s ~ sequence + oSex + s(age,k=4, fx=T) + s(age, k=4, fx = T, by = oSex)"
models <- longTable %>%
    group_by(ROI)%>%
    nest()%>%
    mutate(results=purrr::pmap(list(data,model_formula,this_label = ROI, pbootstrap = F, longPlot = T),.f=gamm_model))
```

# Puberty effects
```{r puberty,eval=F}
# model_formula <- "R2s ~ sequence + oSex + RACE + s(age,k=4, fx=T) + s(age, k=4, fx = T, by = oSex)"
for (roi in c("Caudate","Putamen","Accumbens_Area")) {
  model_formula <- sprintf("%s ~ sequence + tanner_pubic_grp* oSex + (1|bblid)",roi)
  thisTable <- dataTable %>%
    filter(tanner_age_diff<1)
  
  thisTable$tanner_girl_3 <- ordered(thisTable$tanner_girl_3,levels = c(1,2),labels = c("Yes","No"))
  
  # model <- lmer(as.formula(model_formula), data = thisTable)
  # print(anova(model))
  # print(plot_model(model,type = "int"))
  
  
  model_formula <- sprintf("%s ~  tanner_girl_3 + s(age, k = 4) ",roi)
  model <- gamm(as.formula(model_formula), random = list(bblid=~1), data = thisTable, subset = thisTable$oSex=="female")
  print(summary(model$gam))
  b<-getViz(model$gam)
  print(plot(b, allTerms = T),pages = 1)
  print(BIC(model$lme))
  
}

```

## 2D smooth with additional main effects and tensor product smooth, `ti`: `ti(age) + ti(Psychosis) + ti(age,Psychosis)`

From documentation: 
This model specifies a main effects + interaction structure such as:
`y ~ ti(x) + ti(z) + ti(x,z)`  

`ti` is the proper way of specifying an interaction term in the context of included main effect terms:  

"This functional ANOVA decomposition is supported by ti terms, which produce tensor product interactions from which the main effects have been excluded, under the assumption that they will be included separately. For example the ~ ti(x) + ti(z) + ti(x,z) would produce the above main effects + interaction structure. This is much better than attempting the same thing with sor te terms representing the interactions (although mgcv does not forbid it). Technically ti terms are very simple: they simply construct tensor product bases from marginal smooths to which identifiability constraints (usually sum-to-zero) have already been applied: correct nesting is then automatic (as with all interactions in a GLM framework). See Wood (2017, section 5.6.3)."  
  
## Clinical Variables
We are looking at a few models:
Age*sex effects on clin
Age*Clin effects on Brain controlling for sex
Age*Clin effects on Brain separated by sex
```{r Clinical, results="asis",warning=F,eval=F}
# clin_vars <- c("Overall_Psychopathology_SIMPLE","Psychosis"),"Psychosis1_SIMPLE","Psychosis2_SIMPLE","Psychosis3_SIMPLE","Psychosis4_SIMPLE")#,"Depression_SIMPLE","Mania_SIMPLE") #"Depression","Mania"
clin_vars <- c("Overall_Psychopathology_SIMPLE","Mania_SIMPLE","Psychosis","Depression","Depression_SIMPLE") #"Depression","Mania"
for (cv in clin_vars) {
  cat(sprintf("\n\n### Results for %s",cv))
  
  ## First the age models
  # model_formula <- sprintf("%s ~ oSex + timepoint + s(age,k=4, fx=T) + s(age, k=4, fx = T, by = oSex)",cv)
  # ## For now use the same exclusions as with R2*
  # models <- dataTable %>%
  #   filter(scan2cnbmonths<6) %>%
  #   gamm_model(.,model_formula,
  #              this_label = cv,
  #              smooth_var = "age",
  #              group_var = "bblid",
  #              int_var = 'oSex',
  #              pbootstrap = F,
  #              longPlot = F)
  
  # Overall
   model_formula <- sprintf("R2s ~ sequence + timepoint + sex + ti(age, k=4, fx = T) + ti(%s, k=4, fx = T) + ti(%s,age, k=4, fx = T)",cv,cv)
  # model_formula <- sprintf("R2s ~ timepoint + sex + s(age, k=4, fx = T)  + s(age, k=4, fx = T, by = %s)",cv)
    # model_formula <- sprintf("R2s ~ sequence + timepoint + oSex + ti(%s, k=4, fx = T) + ti(%s, k=4, fx = T, by = oSex)",cv,cv)

   thisTab<-longTable[longTable[,cv]!=min(longTable[,cv],na.rm = T), ]
# weight_var = "R2s_cv",
  models <- longTable %>%
      filter(scan2cnbmonths<6) %>%
    filter(R2s>0&R2s<40) %>%
      group_by(ROI)%>%
      nest()%>%
      mutate(results=purrr::pmap(.f=gamm_model,
                                 list(data,model_formula,
                                      smooth_var = "age",
                                      int_var = cv,
                                      group_var = "bblid",
                                      this_label = ROI,
                                      pbootstrap = F)))
##weight_var = "R2s_sd",
  # Male female
  # model_formula <- sprintf("R2s ~ ti(age, k=4, fx = T) + ti(%s, k=4, fx = T) + ti(age,%s, k=4, fx = T)",cv,cv)
  # models <- longTable %>%
  #     filter(GOOD %in% c("1","2") & R2s>0 & R2s <40 & age < 50 & scan2cnbmonths<6) %>%
  #     group_by(ROI,sex)%>%
  #     nest()%>%
  #     unite("ROI_SEX",c(ROI,sex),sep = "_") %>%
  #     mutate(results=purrr::pmap(.f=gamm_model,
  #                                list(data,model_formula,
  #                                     smooth_var = "age",
  #                                     int_var = cv,
  #                                     group_var = "bblid",
  #                                     this_label = ROI_SEX,
  #                                     pbootstrap = F)))
}

```

##SES
###SES and cognition
```{r ses_cog, results="asis",warning=F,eval=F}
env_vars <- colnames(dataTable%>%select(contains("env"),neighborhoodCrime))
cog_vars <- c("NAR_Overall_Accuracy","NAR_Overall_Efficiency","NAR_F2_Social_Cog_Accuracy","NAR_F1_Social_Cognition_Efficiency","NAR_F1_Exec_Comp_Cog_Accuracy","NAR_F3_Executive_Efficiency","NAR_F4_Memory_Efficiency","mpraxis_mp2rtcr")

for (cv in env_vars) {
  cat(sprintf("\n\n### Results for %s",cv))
  
  for (cog in cog_vars) {
    # model_formula <- sprintf("%s ~ timepoint + oSex + oRace_bwo + s(age, k=4, fx = T) + s(age, by = %s, k=4, fx = T)",cog,cv,cv)
    model_formula <- sprintf("%s ~ timepoint + oSex + oRace_bwo + %s + s(age, k=4, fx = T) ",cog,cv)
    
    models <- dataTable %>%
      filter(scan2cnbmonths < 6) %>%
      gamm_model(
        .,
        model_formula,
        this_label = cog,
        smooth_var = "age",
        group_var = "bblid",
        int_var = "oSex",
        pbootstrap = T
      )

  }
}

```

```{r ses, results="asis",warning=F,eval=F}
# env_vars <- colnames(dataTable%>%select(contains("env"),neighborhoodCrime))
env_vars <- colnames(dataTable%>%select(contains("env")))
longTable$envHouseholds[longTable$envHouseholds>2.5 ]<- NA
longTable$weights<- 1/longTable$R2s_cv
for (cv in env_vars) {
  cat(sprintf("\n\n\n### Results for %s\n",cv))  
  
  # model_formula <- sprintf("R2s ~ sequence + timepoint + oSex + oRace_bwo + ti(age, k=4, fx = T) +ti(%s, k=3, fx = T) + ti(age, %s, k=3, fx = T)",cv,cv)
  
  # model_formula <- sprintf("R2s ~ sequence + timepoint + oSex + oRace_bwo + Efficiency_Factor*%s + s(age, k=4, fx = T)",cv)
  
  # model_formula <- sprintf("R2s ~ sequence + timepoint + oSex + s(age, k=4, fx = T)  + s(age, by = %s, k=3, fx = T)",cv,cv)

  # model_formula <- sprintf("R2s ~ sequence + timepoint + oSex + oRace_bwo + %s + I(%s^2) + s(age, k=4, fx = T)",cv,cv) # works
  
  model_formula <- sprintf("R2s ~ sequence + timepoint + oSex + s(age, k=4, fx = F) + s(%s, k=4, fx = F)",cv,cv)
  
  # weight_var = "weights",
  models <- longTable %>%
    filter(RACE == 1) %>%
    group_by(ROI)%>%
    nest()%>%
    mutate(results=purrr::pmap(.f=gamm_model,
                               list(data,model_formula,
                                    smooth_var = cv,
                                    int_var = "age",
                                    group_var = "bblid",
                                    this_label = ROI,
                                    pbootstrap = F)))
  
  #  # Male female
  # model_formula <- sprintf("R2s ~ sequence + timepoint + oRace_bwo + s(age, k=4, fx = T) + s(age, by = %s, k=4, fx = T)",cv,cv)
  # models <- longTable %>%
  #     group_by(ROI,sex)%>%
  #     nest()%>%
  #     unite("ROI_SEX",c(ROI,sex),sep = "_") %>%
  #     mutate(results=purrr::pmap(.f=gamm_model,
  #                                list(data,model_formula,
  #                                     smooth_var = "age",
  #                                     int_var = cv,
  #                                     group_var = "bblid",
  #                                     this_label = ROI_SEX,
  #                                     pbootstrap = F)))
}

```


## Cognitive Variables
Run the models:
```{r Cognitive, results="asis",warning=F, eval = T}
#skip these for now: "F1_Exec_Comp_Cog_Accuracy","F2_Social_Cog_Accuracy","F3_Memory_Accuracy","F1_Slow_Speed","F2_Memory_Speed","F3_Fast_Speed", "Overall_Accuracy","Overall_Speed","Overall_Efficiency","NAR_F3_Memory_Accuracy","NAR_F4_Memory_Efficiency","NAR_F1_Exec_Comp_Cog_Accuracy","NAR_F2_Social_Cog_Accuracy","NAR_F1_Exec_Comp_Cog_Accuracy","NAR_F3_Executive_Efficiency","NAR_F4_Memory_Efficiency"

cog_vars <- c("NAR_Overall_Accuracy","NAR_Overall_Efficiency","NAR_F2_Social_Cog_Accuracy","NAR_F1_Social_Cognition_Efficiency","mpraxis_mp2rtcr")

for (cv in cog_vars) {
  cat(sprintf("\n### Results for %s\n",cv))
  
  # ## First the age models
  # model_formula <- sprintf("%s ~  timepoint + oSex + s(age,k=4, fx=T) + s(age, k=4, fx = T, by = oSex)",cv)
  # ## For now use the same exclusions as with R2*
  # models <- dataTable %>%
  #   filter(scan2cnbmonths<6) %>%
  #   gamm_model(.,model_formula,
  #              this_label = cv,
  #              smooth_var = "age",
  #              group_var = "bblid",
  #              int_var = 'oSex',
  #              pbootstrap = F,
  #              longPlot = F)
  # 

  # model_formula <- sprintf("R2s ~ timepoint + sequence +  sex + ti(age, k=4, fx = T) + ti(%s, k=4, fx = T) + ti(age,%s, k=3, fx = T)",cv,cv)

  model_formula <- sprintf("R2s ~ timepoint + oSex + s(age, k=4, fx = F) + s(%s, k=4, fx = F)",cv)

  thisTable <- longTable
  if (str_detect(cv,"pcet")) {
    thisTable$exclusions <- thisTable$scan2cnbmonths>6 | thisTable$pcet_rtcr>5500 #There are some outliers here
  } else if (cv == "mpraxis_mp2rtcr") {
    thisTable$exclusions <- thisTable$scan2motormonths>6 | thisTable$mpraxis_mp2rtcr>1500
  }
  else {
    thisTable$exclusions <- thisTable$scan2cnbmonths>6
  }
  
  # #weight_var = "R2s_cv",
  #int_var = cv,
  models <- thisTable %>%
      group_by(ROI)%>%
      nest()%>%
      mutate(results=purrr::pmap(list(data,model_formula,
                                      this_label = ROI,
                                      smooth_var = "age",
                                      int_var = cv,
                                      group_var = "bblid",
                                      pbootstrap = F),
                                 .f=gamm_model))
  
  model_formula <- sprintf("R2s ~ timepoint + sex + s(age, k=4, fx = F) + s(age, by = %s, k=4, fx = F)",cv,cv)
  
  models <- thisTable %>%
      group_by(ROI)%>%
      nest()%>%
      mutate(results=purrr::pmap(list(data,model_formula,
                                      this_label = ROI,
                                      smooth_var = "age",
                                      int_var = cv,
                                      group_var = "bblid",
                                      pbootstrap = F),
                                 .f=gamm_model))
  # 
  # Male female
  model_formula <- sprintf("R2s ~ timepoint + s(age) + s(age, by = %s, k=4)",cv)
  models <- longTable %>%
      group_by(ROI,sex)%>%
      nest()%>%
      unite("ROI_SEX",c(ROI,sex),sep = "_") %>%
      mutate(results=purrr::pmap(.f=gamm_model,
                                 list(data,model_formula,
                                      smooth_var = "age",
                                      int_var = cv,
                                      group_var = "bblid",
                                      this_label = ROI_SEX,
                                      pbootstrap = F)))
}

```

## Tanner cog
Run the models:
```{r Tanner Cognitive, results="asis",warning=F, eval = F}
#skip these for now: "F1_Exec_Comp_Cog_Accuracy","F2_Social_Cog_Accuracy","F3_Memory_Accuracy","F1_Slow_Speed","F2_Memory_Speed","F3_Fast_Speed", "Overall_Accuracy","Overall_Speed","Overall_Efficiency","NAR_F3_Memory_Accuracy","NAR_F4_Memory_Efficiency","NAR_F1_Exec_Comp_Cog_Accuracy","NAR_F2_Social_Cog_Accuracy",

cog_vars <- c("NAR_Overall_Accuracy","NAR_Overall_Efficiency","NAR_F2_Social_Cog_Accuracy","NAR_F1_Social_Cognition_Efficiency","NAR_F1_Exec_Comp_Cog_Accuracy","NAR_F3_Executive_Efficiency","NAR_F4_Memory_Efficiency","mpraxis_mp2rtcr")

for (cv in cog_vars) {
  cat(sprintf("\n### Results for %s\n",cv))

  thisTable <- dataTable
  if (str_detect(cv,"pcet")) {
    thisTable$exclusions <- thisTable$scan2cnbmonths>6 | thisTable$pcet_rtcr>5500 #There are some outliers here
  } else if (cv == "mpraxis_mp2rtcr") {
    thisTable$exclusions <- thisTable$scan2motormonths>6 | thisTable$mpraxis_mp2rtcr>1500
  }
  else {
    thisTable$exclusions <- thisTable$scan2cnbmonths>6
  }

  for (roi in c("Putamen","Caudate","Accumbens_Area")) {
    model_formula <- sprintf("%s ~ timepoint + sequence + tanner_pubic_grp*%s + (1|bblid) ",roi,cv)
    # g<-gamm(as.formula(model_formula), data = thisTable, random = list(bblid=~1),
    #         subset = thisTable$oSex=='female' & !thisTable$exclusions)
    g<-lmerTest::lmer(as.formula(model_formula), data = thisTable,
            subset = thisTable$oSex=='female' & !thisTable$exclusions)
    print(summary(g))
    # b <- getViz(g$gam)
    # var_plot <- plot(b,allTerms = T) + 
    # l_ciPoly() +
    # l_fitRaster() + l_fitContour() + 
    # l_points() +  l_ciBar() +
    # l_fitPoints(size = 1, col = 2) + l_fitLine() +
    # labs(title = paste(roi,'_',cv))
    # print(var_plot, pages =1)
    print(plot_model(g,type = "int"))
    
  }
}

```

## IQ Variables
Run the models:
```{r IQ, results="asis",eval=F}
cog_vars <- c("wrat4_std","wrat4_raw") #"wrat3_raw",
for (cv in cog_vars) {
  cat(sprintf("/n/n### Results for %s",cv))
  model_formula <- sprintf("R2s ~ sex + ti(age, k=4, fx = T) + ti(%s, k=4, fx = T) + ti(age,%s, k=4, fx = T)",cv,cv)
  thisTable <- longTable
  if (str_detect(cv,"wrat4")) {
    thisTable$exclusions <- thisTable$scan2wratmonths>6 | thisTable$age>=40 #There is one old person
  } else {
    thisTable$exclusions <- thisTable$scan2wratmonths>6
  }
  models <- thisTable %>%
      group_by(ROI)%>%
      nest()%>%
      mutate(results=purrr::pmap(list(data,model_formula,
                                      this_label = ROI,
                                      smooth_var = "age",
                                      int_var = cv,
                                      group_var = "bblid", 
                                      pbootstrap = T),
                                 .f=gamm_model))
}

```

