---
title: "Age and Age*Cognition GAMM Models"
author: "Bart"
date: "6/25/2019"
output:
  html_document: default
  toc: true
  # pdf_document: default
---

# Modeling the effect of continuous interactions of covariates with `age` on `R2s`
This code implements GAMM models for continuous variables including continuous x continuous interactions.
Significance is tested using parametric bootstrapping.

---

```{r setup, include=FALSE}
## Load Libraries
require(ggplot2)
require(gridExtra)
require(tidyverse)
require(mgcv)
require(gamm4)
require(mgcViz)
require(pbkrtest)
require(itsadug)
library(broom)
library(kableExtra)
library(parallel)
library(scales)
source('/Users/larsenb/software/ComBatHarmonization-master/R/scripts/utils.R')
knitr::opts_knit$set(root.dir = "/data/jux/BBL/projects/brain_iron/scripts/PublicationScripts")
theme_set(theme_classic())
```

```{r make cluster, include=F}
#This is creating a local cluster that can speed up the bootstrapping by parallel processing
cl <- makeCluster(rep("localhost",20))
```
 
## Relevant functions:
### GAMM modeling
```{r gamm}
# This function:
# 1. executes the GAMM model,
# 2. sends output to the parametric bootstrap (if requested),
# 3. prints a regression table, and 
# 4. sends the model to the visualizer for plotting.

gamm_model <- function(df, model_formula, this_label, smooth_var, int_var = NULL,weight_var = NULL,group_var, pbootstrap = F, longPlot = F, model_test = T){
  cat(sprintf("\n\n### Results for %s\n",this_label))
  if (is.null(weight_var)) {
    df$weight <- 1 #if no weighting variable is provided, weight all obs equally.
  } else {
    df$weight <- unlist(df[,weight_var]) # Use weight variable if provided.
  }

  model_formula <- as.formula(model_formula)
  if(!"exclusions" %in% colnames(df))  {
    df$exclusions <- FALSE; #there is no exclusions column so make one that excludes none
  }

  g1<-gamm(model_formula,
           data=df,
           random = list(bblid =~ 1),
           subset = exclusions == F,
           weights = weight)
  
  if (model_test == T){
    if (pbootstrap == T) {
      #Send to bootstrap function
      g1$pb<-pboot(g1) 
      #Print a table that shows the bootstrap outcome
      print(g1$pb %>%
        summary() %>%
        .$test %>%
        as.data.frame() %>%
        kable(caption = sprintf("Parametric Bootstrap test for %s",this_label)) %>%
        kable_styling(full_width = F, position = "left",bootstrap_options = c("striped"))
      )
      
      if (isTRUE(all.equal(g1$pb$bestmod,model_formula))) {
        cat("The initial (more complicated) model is best")
        g <- g1
        
        #This next part is no longer implemented (refit the model using unfixed degrees of freedom). Effective part is commented out below.
        if (str_detect(deparse(model_formula),"F1_Social_Cognition_Efficiency") &this_label == "Right_Pallidum_male") {
          plot_formula <- model_formula
        } else {
        plot_formula <- as.formula(gsub(", fx = T","",deparse(model_formula)))
        }
        cat(deparse(plot_formula))
        plotg<-g
        # plotg <- gamm(plot_formula,
        #               data = df,
        #               random = list(bblid =~1),
        #               subset = exclusions == F)
      } else {
        cat("The simpler model is best")
        
        g <-gamm(as.formula(g1$pb$bestmod),
                 data=df,
                 random = list(bblid =~ 1),
                 subset = exclusions == F,
                 weights = weight)
        
        #Again, this part not implemented (model not refit with unfixed df)
        plot_formula <- as.formula(gsub("ti\\(",'te\\(',deparse(g$gam$formula)) %>% gsub(", fx = T", "", .))
        plotg<-g
        # plotg <-gamm(plot_formula,
        #          data=df,
        #          random = list(bblid =~ 1),
        #          subset = exclusions == F)
      }
    } else {
      if (!is.null(int_var)) {
        # We are not bootstrapping, but there is an interaction variable
        s<-summary(g1$gam)
        if (s$s.table[grep(x=rownames(s$s.table),pattern = int_var),"p-value"] <.05)  {
          #Checked if interaction is sig, if so keep in the model
          g <- g1
          plot_formula <- as.formula(gsub(", fx = T", "", deparse(model_formula)))
          plotg <- g
        } else {
          #Interaction is not sig, remove from the model
          cat("The simpler model is best")
          thisResp <- as.character(g1$gam$terms[[2]])
          theseVars <- attr(terms(model_formula),"term.labels")
          new_formula <- reformulate(theseVars[0:(length(theseVars)-1)],response = thisResp)
          
          g <-gamm(as.formula(new_formula),
                   data=df,
                   random = list(bblid =~ 1),
                   subset = exclusions == F,
                   weights = weight)
          plot_formula <- as.formula(gsub("ti\\(",'te\\(',deparse(g$gam$formula)) %>% gsub(", fx = T", "", .))
          plotg<-g
      }
      } else {
        #There is no interaction term, just plot.
        g <- g1
          plot_formula <- as.formula(gsub(", fx = T", "", deparse(model_formula)))
          plotg <- g
      }
    }
  } else {
    g <- g1
    plotg<-g
  }

  g$gam$data<-df %>%
    filter(exclusions == F)
  
  #Display model results:
  
  s_tidytable<- tidy(g$gam)
  p_tidytable <- tidy(g$gam,parametric = T)
  snames = names(s_tidytable)
  pnames = names(p_tidytable)
  names(s_tidytable)=pnames
  thisBIC <- BIC(g$lme)
  numObs <- g$lme$dims$N
  g$BIC <- thisBIC
  stattable <- rbind(p_tidytable,snames,s_tidytable) %>%
    kable(caption = sprintf("Regression table from gamm in %s, BIC = %1.2f, obs = %d",this_label,thisBIC,numObs)) %>% 
    kable_styling(full_width = F, position = "left")
  print(stattable)
  
  #Send final model to visualizer:
  if (s_tidytable$p.value[nrow(s_tidytable)]<.05) {
    if (longPlot == T) {
      g$pl <- longitudinal_plot(g,plabels = this_label)
    } else {
      g$pl <- visualize_models(plotg,plabels = this_label, smooth_var = smooth_var, int_var = int_var, group_var = group_var)
    }
  }
  #Return result object
  result <- g
  
  return(result)
}
```

### Bootstrap procedure
This procedure is lifted from https://github.com/PennBBL/groupAnalysis/wiki/Model-Comparison-Using-Parametric-Bootstrap
```{r include=T,opts.label = "Bootstrap Function"}
## Parametric bootstrap of likelihood ratio test for nested models
pboot <- function(modelobj){
  numsims <- 500

  df <- modelobj$gam$model
  thisResp <- as.character(modelobj$gam$terms[[2]])
  f1 <- modelobj$gam$formula
  theseVars <- attr(terms(f1),"term.labels")
  f2 <- reformulate(theseVars[0:(length(theseVars)-1)],response = thisResp)
  
  g1 <- gam(f1,data = df,weights = `(weights)`)
  g2 <- gam(f2,data = df,weights = `(weights)`)

  mat1 <- model.matrix(g1)
  mat2 <- model.matrix(g2)

  bblid<-df$bblid
  y <- df[,thisResp]
  w <- unlist(df[,"(weights)"])
  
  m1 <- lmer(y ~ -1 + mat1 + (1|bblid),weights = w)
  m2 <- lmer(y ~ -1 + mat2 + (1|bblid),weights = w)
  refdist <- PBrefdist(m1, m2, nsim=numsims)#, cl=cl)
  pb <- PBmodcomp(m1, m2, ref = refdist)
  int_pval <- pb$test["PBtest","p.value"]
  if (int_pval < .05) {
    pb$bestmod <- f1
  } else {
    pb$bestmod <- f2
  }
  return(pb)
}
```

```{r visual func, include=FALSE}
# Func to visualize model outputs
visualize_models <- function(modobj,smooth_var, int_var ,group_var, plabels = NULL,check_diagnostics = F){
  if (any(class(modobj)=="gam")) {
    model <- modobj
  } else if (class(modobj$gam)=="gam") {
    model <- modobj$gam
  } else {
    stop("Can't find a gam object to plot")
  }

  ## Plot using mgcViz functions
  # Uses premade function to get all terms plotted
  b <- getViz(model)
  var_plot <- plot(b,allTerms = T) + 
    l_ciPoly() +
    l_fitRaster() + l_fitContour() + 
    l_points() +  l_ciBar() +
    l_fitPoints(size = 1, col = 2) + l_fitLine() +
    labs(title = plabels)
  # mtext(plabels, outer = TRUE, cex = 1.5)

  print(var_plot,pages = 1) 

  ## Generate custom line plot
  np <- 10000 #number of predicted values
  df = model$model

  theseVars <- attr(model$terms,"term.labels")
  varClasses <- attr(model$terms,"dataClasses")
  thisResp <- as.character(model$terms[[2]])

  if (!is.null(int_var)) {
    if (!any(grepl(x=as.character(model$formula),pattern = int_var))) {
      return()
    }
   vg<-vis.gam(model,view = c(smooth_var,int_var),plot.type = "persp",theta = 45,phi = -5,color = "topo")
   print(vg)
    switch (varClasses[int_var],
      "numeric" = {
        q <- quantile(df[,int_var],probs = c(.05,.95)) #pick 5% and 95% to plot
        bigq <- q[[2]]
        smallq <- q[[1]]
        values <- c(bigq,smallq)
        labs <- c(sprintf("high (%1.2f)",bigq),sprintf("low (%1.2f)",smallq))

        #Get plot color break values
        # q <- quantile(df[,int_var],probs = c(0,.1,.5,.9,1))
        # break_values <- unname(q)
        # break_labels <- names(q)
        # limit_values <- c(q[[1]],q[[length(q)]])

        q <-quantile(rescale(df[,int_var],c(0,1)),probs = c(0,.5,1))
        limit_values <- c(q[[1]],q[[length(q)]])
        midpoint_val <- unname(q[[2]])
        cbar_vals <- unname(q)
        grad_fill = T
      },
      "factor" = {
        labs <- levels(df[,int_var])
        values <- levels(df[,int_var])
        grad_fill = F
      },
      "ordered" = {
        labs <- levels(df[,int_var])
        values <- levels(df[,int_var])
        grad_fill = F
      }
    )
    labPred <- data.frame(init = rep(0,np*length(labs)))
    labPred[,int_var] = rep(values,each = np)
    labPred$lab = rep(labs,each = np)
    labPred <- labPred[,names(labPred) !="init"]
    thisPred <- data.frame(init = rep(0,np))
    for (v in c(1:length(theseVars))) {
      thisVar <- theseVars[[v]]
      thisClass <- varClasses[thisVar]
      if (thisVar == smooth_var) {
        thisPred[,smooth_var] = seq(min(df[,smooth_var],na.rm = T),max(df[,smooth_var],na.rm = T), length.out = np)
      } else if (v == int_var) {
        next
      } else {
        switch (thisClass,
            "numeric" = {thisPred[,thisVar] = median(df[,thisVar])},
            "factor" = {thisPred[,thisVar] = levels(df[,thisVar])[[1]]},
            "ordered" = {thisPred[,thisVar] = levels(df[,thisVar])[[1]]}
              )
      }
    }

    thisPred <- thisPred %>% select(-init)
    thisPred <- do.call("rbind", replicate(length(labs), thisPred, simplify = FALSE))

    pred <- cbind(labPred,thisPred)
    p<-data.frame(predict(modobj$gam,pred,se.fit = T))
    pred <- cbind(pred,p)
    pred$selo <- pred$fit - 2*pred$se.fit
    pred$sehi <- pred$fit + 2*pred$se.fit
    pred[,group_var] = NA
    pred[,thisResp] = 1

    low_color = "#7b3294"
    high_color = "#008837"
      #scale_color_gradientn(colors = c("blue4","blue","linen","red","red4"),limits = limit_values,breaks = break_values, labels = break_labels)
    #scale_fill_manual(values = c("red","blue")) +
    if (grad_fill == T) {
      p1 <- ggplot(data = df, aes_string(x = smooth_var,y = thisResp, color = int_var)) +
      geom_point(alpha = .5) + geom_line(aes(group = bblid),alpha = .5) +
      scale_color_gradientn(colors = c(low_color,high_color), values = cbar_vals) +
      geom_ribbon(data = pred,aes_string(x = smooth_var , ymin = "selo",ymax = "sehi", fill = "lab"),alpha = .5, linetype = 0) +
      scale_fill_manual(values = c(high_color,low_color)) +
      geom_line(data = pred,aes_string(x = smooth_var, y = "fit",group = "lab"),size =1) +
      labs(title = plabels, y = "R2*", x = "Age (years)", col = int_var)
    } else {
    p1 <- ggplot(data = df, aes_string(x = smooth_var,y = thisResp, color = int_var)) +
      geom_point(alpha = .5) + geom_line(aes(group = bblid),alpha = .5) +
      scale_color_brewer(type = "qual",palette = 6) +
      geom_ribbon(data = pred,aes_string(x = smooth_var , ymin = "selo",ymax = "sehi", fill = int_var),alpha = .5, linetype = 0) +
      scale_fill_brewer(type = "qual",palette = 6) +
      geom_line(data = pred,aes_string(x = smooth_var, y = "fit",group = int_var,color = int_var),size =1) +
      labs(title = plabels, y = "R2*", x = "Age (years)", col = int_var)
    }
    if (str_detect(plabels,"Accumbens")) {
      p1 <- p1 + ylim(10,35)
    } else if (str_detect(plabels,"Pallidum")) {
      p1 <- p1 + ylim(12,40)
    } else if (any(str_detect(plabels,c("Putamen","Caudate")))) {
      p1 <- p1 + ylim(10,25)
    }
  print(p1)
  } else {

  # line plot
    thisPred <- data.frame(init = rep(0,np))

    for (v in c(1:length(theseVars))) {
      thisVar <- theseVars[[v]]
      thisClass <- varClasses[thisVar]
      if (thisVar == smooth_var) {
        thisPred[,smooth_var] = seq(min(df[,smooth_var],na.rm = T),max(df[,smooth_var],na.rm = T), length.out = np)
      } else {
        switch (thisClass,
            "numeric" = {thisPred[,thisVar] = median(df[,thisVar])},
            "factor" = {thisPred[,thisVar] = levels(df[,thisVar])[[1]]},
            "ordered" = {thisPred[,thisVar] = levels(df[,thisVar])[[1]]}
              )
      }
    }
    pred <- thisPred %>% select(-init)
    p<-data.frame(predict(modobj$gam,pred,se.fit = T))
    pred <- cbind(pred,p)
    pred$selo <- pred$fit - 2*pred$se.fit
    pred$sehi <- pred$fit + 2*pred$se.fit
    pred[,group_var] = NA
    pred[,thisResp] = 1

    p1 <- ggplot(data = df, aes_string(x = smooth_var,y = thisResp)) +
      geom_point(alpha = .5) + geom_line(aes(group = bblid),alpha = .5) +
      geom_ribbon(data = pred,aes_string(x = smooth_var , ymin = "selo",ymax = "sehi"),alpha = .5, linetype = 0) +
      geom_line(data = pred,aes_string(x = smooth_var, y = "fit"),size =1) +
      labs(title = plabels, y = "R2*", x = smooth_var)
    if (str_detect(plabels,"Accumbens")) {
      p1 <- p1 + ylim(10,35)
    } else if (str_detect(plabels,"Pallidum")) {
      p1 <- p1 + ylim(12,40)
    } else if (any(str_detect(plabels,c("Putamen","Caudate")))) {
      p1 <- p1 + ylim(10,25)
    }
  print(p1)
}
  #
  # var_plot2 <- plot(sm(b,3)) + l_fitRaster(pTrans = function(.p) .p<.05) + l_fitContour() + l_points()
  # print(var_plot2)
  # print(plotRGL(sm(b, 1), fix = c("z" = 0), residuals = F))

  if (check_diagnostics == T) {
    cp <- check(b,
    a.qq = list(method = "tnorm",
                a.cipoly = list(fill = "light blue")),
    a.respoi = list(size = 0.5),
    a.hist = list(bins = 10))
    print(cp)
  }
  return(var_plot)
}
```

```{r long vis, include = FALSE}
# Special case for plotting age and age*sex models. Mostly redundant now that the above function exists, but it works and sets colors differently, so it is still used.
longitudinal_plot <- function(modobj,plabels = NULL){
  df <- modobj$gam$model
  thisResp <- as.character(modobj$gam$terms[[2]])

  pred.male <- data.frame(age = seq(min(df$age,na.rm = T),max(df$age,na.rm = T), length.out = 1000), oSex = 'male',visit = "1",sequence = "B0map_onesizefitsall_v3",oRace_bwo = "1")
  p<-data.frame(predict(modobj$gam,pred.male,se.fit = T))
  pred.male$fit = p$fit
  pred.male$selo = p$fit - 2*p$se.fit
  pred.male$sehi = p$fit + 2*p$se.fit
  pred.male[,thisResp] = 1
  pred.male$bblid=1
  
  pred.female <- data.frame(age = seq(min(df$age,na.rm = T),max(df$age,na.rm = T), length.out = 1000), oSex ='female', visit="1",sequence = "B0map_onesizefitsall_v3",oRace_bwo = "1")
  p<-data.frame(predict(modobj$gam,pred.female,se.fit = T))
  pred.female$fit = p$fit
  pred.female$selo = p$fit - 2*p$se.fit
  pred.female$sehi = p$fit + 2*p$se.fit
  pred.female[,thisResp] = 1
  pred.female$bblid=1


  # geom_point(alpha = .25) +
  p1 <- ggplot(data = df,aes_string(x = "age", y = thisResp, group = "bblid",color = "oSex")) +
    geom_line(alpha = .25) + geom_point(alpha = .25) +
    scale_color_manual(values = c("blue","red")) +
    geom_ribbon(data = pred.male, aes(ymin=selo, ymax=sehi), fill = "blue", alpha = .3, linetype = 0,show.legend = F) +
    geom_line(data = pred.male,aes(x = age, y = fit), color = "blue",size = 1) +
    geom_ribbon(data = pred.female, aes(ymin=selo, ymax=sehi), fill = "red", alpha = .3, linetype = 0,show.legend = F) +
    geom_line(data = pred.female,aes(x = age, y = fit), color = "red",size = 1) +
    labs(title = plabels, y = "R2*", x = "Age (years)", col = "Sex")  + ylim(min(pred.female$selo-.5),NA)
  if (str_detect(plabels,"Accumbens")) {
    p1 <- p1 + ylim(10,30)
  } else if (str_detect(plabels,"Pallidum")) {
    p1 <- p1 + ylim(15,32)
  } else if (any(str_detect(plabels,c("Putamen","Caudate")))) {
    p1 <- p1 + ylim(11,25)
  }
  
  print(p1)
}
```

```{r load data, warning=FALSE, include=FALSE}
# Load the datafile
dataFile <- "/data/jux/BBL/projects/brain_iron/scripts/PublicationScripts/brain_iron_data_TEMPLATE.Rda"
if (file.exists(dataFile)) {
  dataTable <- readRDS(file=dataFile)
}  else {
  source('compileData.R')
  compileData()
  dataTable <- readRDS(file=dataFile)
}

## Filter
### Remove
### 1. Projects with incompatible data (reward)
### 2. Sequences with odd parameters
### 3. Scans that don't pass QA
### 4. A couple scans and timepoints that hae very few observations (for better model fitting)
dataTable <- dataTable %>%
  filter(bblid != 110689)%>%
  filter(!(ProjectName %in% c("DAY2_808799",
                              "FNDM1_810211",
                              "FNDM2_810211",
                              "NEFF_V2",
                              "NEFF_PILOT",
                              "GRMPY_822831",
                              "GRMPY_V2",
                              "GRMPY_V3")
           )
         ) %>% #Not using data from these projects.
  filter(sequence != 'B0map_v4_matchedFOV') %>% # Different voxel size
  filter(sequence != 'B0map_onesizefitsall_v3_T2S') %>% # small number of scans with odd params
  filter(GOOD %in% c("1","2")) %>%
  filter(!timepoint %in% c("4")) %>% # Only 5 visits at timepoint 4, may cause issues for modeling
  filter(sequence != 'b0map_v4') %>% #Very few scans, potentially issue for model fitting
  filter(age<35) # not necessary, all are already under 35

longTable <- dataTable %>%
    gather(key = "ROI",value="R2s",Accumbens_Area,Putamen,Caudate,Pallidum)

rois <- c("Caudate","Putamen","Accumbens_Area")
```

---
# Developmental effects

Fit nonlinear age effect and check for age*sex interaction (factor smooth interaction: `s(age, by = oSex)`)
oSex is Sex specified as an ordered factor to appropriately test for the interaction (female against male reference)
```{r developmental, results="asis",eval=T}
model_formula <- "R2s ~ sequence + oSex + s(age,k=4, fx=T) + s(age, k=4, fx = T, by = oSex)"
models <- longTable %>%
    group_by(ROI)%>%
    nest()%>%
    mutate(results=purrr::pmap(list(data,model_formula,this_label = ROI, pbootstrap = T, longPlot = T),.f=gamm_model))
```

## Modeling of continuous*continuous interactions tests two possible models.  
We compare an additive (main effects + interaction) bivariate smooth model and a varying coefficient model (details below).
The best model is chosen via the smallest BIC.
After the best interaction  model is selected, the significance of the interaction is tested with a parametric bootstrap likelihood ratio test. This test compares the model with the interaction term against a simpler nested model with main effects only. If the interaction model is significantly better, we keep that model. If not, the final model is the simpler model with no interaction.  

### 2D smooth with additional main effects and tensor product smooth, `ti`: `ti(age) + ti(Cognition) + ti(age,Cognition)`

From documentation: 
This model specifies a main effects + interaction structure such as:
`y ~ ti(x) + ti(z) + ti(x,z)`  

`ti` is the proper way of specifying an interaction term in the context of included main effect terms:  

"This functional ANOVA decomposition is supported by ti terms, which produce tensor product interactions from which the main effects have been excluded, under the assumption that they will be included separately. For example the ~ ti(x) + ti(z) + ti(x,z) would produce the above main effects + interaction structure. This is much better than attempting the same thing with s or te terms representing the interactions (although mgcv does not forbid it). Technically ti terms are very simple: they simply construct tensor product bases from marginal smooths to which identifiability constraints (usually sum-to-zero) have already been applied: correct nesting is then automatic (as with all interactions in a GLM framework). See Wood (2017, section 5.6.3)."  

### Varying coefficient model (using `by =`)

This will make the fit linear (rather than non-linear smooth) in the `by` variable
From documentation: 
"When using `by` with a numberic covariate, "the by argument ensures that the smooth function gets multiplied by covariate z"
  
## Cognitive Variables
Run the models:
```{r Cognitive, results="asis",warning=F, eval = T}
cog_vars <- c("NAR_Overall_Accuracy","NAR_Overall_Efficiency","NAR_F2_Social_Cog_Accuracy","NAR_F1_Social_Cognition_Efficiency","mpraxis_mp2rtcr","wrat4_std")
## First the developmental models
    # model_formula <- sprintf("%s ~ sequence + timepoint + oSex + s(age,k=4, fx=T) + s(age, k=4, fx = T, by = oSex)",cv)
    # models <- dataTable %>%
    #   filter(scan2cnbmonths<6) %>%
    #   gamm_model(.,model_formula,
    #              this_label = cv,
    #              smooth_var = "age",
    #              group_var = "bblid",
    #              int_var = 'oSex',
    #              pbootstrap = T,
    #              longPlot = F)
    
for (r in rois) {
  cat(sprintf("\n## Results for %s\n",r))
  for (cv in cog_vars) {
    cat(sprintf("\n### %s\n",cv))
    thisTable <- dataTable
    if (cv == "mpraxis_mp2rtcr") {
      thisTable$exclusions <- thisTable$scan2cnbmonths>6 | thisTable$mpraxis_mp2rtcr>1500
    }
    else {
      thisTable$exclusions <- thisTable$scan2cnbmonths>6
    }
    
    # First look at a main effects only model
    add_formula <- sprintf("%s ~ sequence + timepoint + sex + s(age, k=4, fx = T) + s(%s, k=4, fx = T)",r,cv)
    gamm_model(thisTable,
               add_formula,
               this_label = sprintf("%s %s M.E.",r,cv),
               smooth_var = cv,
               group_var = "bblid",
               pbootstrap = F,
               model_test = F)
    
    # Compare the two interaction models
    cat('\n### Comparing interaction models...\n')
    # Bivariate interaction
    bv_formula <- sprintf(
      "%s ~ sequence + timepoint + sex + ti(age, k=4, fx = T) + ti(%s, k=4, fx = T) + ti(age,%s, k=4, fx = T)",
      r,cv,cv)
    # Linear varying coefficient interaction
    vc_formula <- sprintf(
      "%s ~ sequence + timepoint + sex + s(age, k=4, fx = T) + s(age, by = %s, k=4, fx = T)",
      r,cv)
  
    bv <- gamm(as.formula(bv_formula),
               random = list(bblid=~1),
               data = thisTable,
               subset = thisTable$exclusions == 0)
    vc <- gamm(as.formula(vc_formula),
               random = list(bblid=~1),
               data = thisTable,
               subset = thisTable$exclusions == 0)
    bic<-BIC(bv$lme,vc$lme) # get BIC
    bestmod <- gsub(row.names(bic)[which.min(bic$BIC)],pattern = "$lme",replacement = "", fixed = T) #best is min BIC
    switch (bestmod,
      "bv" = {model <- bv},
      "vc" = {model <- vc}
    )
    model_formula <- model$gam$formula
    cat(sprintf("\n\nbest model is %s\n",deparse(model_formula)))
    a <- anova(model$gam)
    print(kable(a$pTerms.table)%>%kable_styling(position = "left"))
    print(kable(a$s.table)%>%kable_styling(position = "left"))
    
    # Now check if the interaction is significant
    gamm_model(thisTable,
               model_formula,
               this_label = sprintf("%s %s final model",r,cv),
               smooth_var = "age",
               int_var = cv,
               group_var = "bblid",
               pbootstrap = F)

  }
}

```

